### 2014-02-28 paper/retrofit.tex
Fixup.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>
one scheduler; rule D is back, rm from formal;

\begin{figure}
  Concurrent, round robin:
\begin{code}
  roundrobin step (it1, it2, ldots)  = it2, ldots, it1
  roundrobin D (it1, it2, ldots)     = it2, ldots
  roundrobin N (it1, it2, ldots)     = it2, ldots
  roundrobin F (it1, it2, ldots)     = it2, ldots, it1
\end{code}
  Sequential:
\begin{code}
  seq step (it1, it2, ldots)     = it1, it2, ldots
  seq N (it1, it2, ldots)        = it1, it2, ldots
  seq D (it)                     = it
  seq D (it1, it2, ldots)        = it2, ldots
  seq F (it1, it2, ldots, itn)   = itn, it1, it2, ldots
\end{code}
\caption{Scheduling policies}
\label{fig:schedule}
\end{figure}

\begin{itemize}
    \item We extend the values, expressions and evaluation contexts of both languages to allow for embeddings terms in one language to be embedded in the other.
    \item We reinterpret |CE| to be evaluation contexts on threadpools, providing definitions for $\mathcal{E}_{\tar{\Sigma}}$ and $\mathcal{E}_{\ifc{\Sigma}}$.  These rules only operate on the first thread in the threadpool, which by convention, is the only thread executing.
    \item We reinterpret |->|, an operation on a single thread, in terms of |.->|, operation on thread pools.  The correspondence is simple: a thread executes a step and then is rescheduled in the thread pool according to schedule policy $\alpha$.  Not all schedulers preserve non-interference, so we provide two specific schedules in Figure~\ref{fig:schedule}.
    \item Finally, we define some rules for scheduling, handling forking threads (which interact with the state of the target language) and intermediating between the borders of the two languages.
\end{itemize}

@@

>>>>

\begin{figure}
  Concurrent, round robin:
\begin{code}
  roundrobin step (it1, it2, ldots)  = it2, ldots, it1
  roundrobin D (it1, it2, ldots)     = it2, ldots
  roundrobin N (it1, it2, ldots)     = it2, ldots
  roundrobin F (it1, it2, ldots)     = it2, ldots, it1
\end{code}
  Sequential:
\begin{code}
  seq step (it1, it2, ldots)     = it1, it2, ldots
  seq N (it1, it2, ldots)        = it1, it2, ldots
  seq D (it)                     = it
  seq D (it1, it2, ldots)        = it2, ldots
  seq F (it1, it2, ldots, itn)   = itn, it1, it2, ldots
\end{code}
\caption{Scheduling policies}
\label{fig:scheduler}
\end{figure}

\begin{itemize}
    \item We extend the values, expressions and evaluation contexts of both languages to allow for embeddings terms in one language to be embedded in the other.
    \item We reinterpret |CE| to be evaluation contexts on threadpools, providing definitions for $\mathcal{E}_{\tar{\Sigma}}$ and $\mathcal{E}_{\ifc{\Sigma}}$.  These rules only operate on the first thread in the threadpool, which by convention, is the only thread executing.
    \item We reinterpret |->|, an operation on a single thread, in terms of |.->|, operation on thread pools.  The correspondence is simple: a thread executes a step and then is rescheduled in the thread pool according to schedule policy $\alpha$.  Not all schedulers preserve non-interference, so we provide two specific schedules in Figure~\ref{fig:scheduler}.
    \item Finally, we define some rules for scheduling, handling forking threads (which interact with the state of the target language) and intermediating between the borders of the two languages.
\end{itemize}

@@

In this setting, it is also clear that exceptions should not cross boundaries,
as seen in |toLabeled l fail; true|, which evaluates to |true| no matter even in
the event of an exception inside of the |toLabeled| block:
